\documentclass[a4,useAMS,usenatbib]{mn2e}

\usepackage{color}
\usepackage{epsfig}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}

%%%%% ASTRO-PH formatting
\setlength{\topmargin}{-0.625in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

\newcommand*{\chck}[1]{{\color{red}$<$#1$>$}}

\def\degree{$^{\circ}$}
\def\herschel{{\em Herschel}}
\def\spire{\herschel-SPIRE}
\def\higal{Hi-GAL}
\def\pacs{\herschel-PACS}
\def\spitzer{{\em Spitzer}}
\def\mic{$\umu$m}

\title{Clouds Paper}

\author[The world]{R.~Simpson$^1$, c.~J.~Lintott$^1$, C.~E.~North$^2$ et al.
\\
$^1$Oxford
$^2$Cardiff
}
\begin{document}

\date{Accepted 20xx. Received 20xx.}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2012}

\maketitle

\label{firstpage}

\begin{abstract}
Abstract
\end{abstract}

\section{Introduction}
Infrared dark clouds (IRDCs) were first observed as dark regions
silhouetted against the mid-infrared (MIR) background
\citep{Wilcock2012a} by \emph{Infrared Space Observatory} \citep{ISO}
and \emph{Midcourse Space Experiment} \citep{ISO}. Subsequent
observations showed them to have low temperatures and high densities
($T\lesssim$\,K, $n_H > 10^5$\,cm$^-3$,
e.g.~\citet{Egan98,Carey98,HennebellePerault02}). The IRDC absorbs the
background light and causes a dip in the MIR sky brightness. They are
thought to be the earliest observable formation stages high-mass stars
and stellar clusters.

Following the initial surveys, the MIPSGAL and GLIMPSE surveys used
the IRAC and MIPS instuments on \spitzer allowed the compilation of
larger and more complete catalogues (e.g. \citet{PF09}). With MIR data
alone, however, it is impossible to distinguish this absorption from a
region of inherently lower background emission. Far-Infared (FIR)
observations allow IRDCs, which appear bright at wavelengths above
24\,\mic, to be distinguished from regions of lower emission, which
remain dark -- a 'hole in the sky'
(e.g. \citet{Stanke2010_NGC1999}). It is important to identifying
which of the candidate IRDCs in the catalogues are 'true' dark clouds,
and which are simply holes in the sky. Such interlopers would bias any
statistical studies of IRDCs based on these catalogues.

The HIGAL survey, using the SPIRE and PACS instrument on-board
the \emph{Herschel Space Observatory}, covered a $|b|\le 1\deg$ strip
of the entire Galactic Plane at 70, 160, 250, 350 and 500\,\mic. Using
the 8 and 24\,\mic\ data from GLIMPSE and MIPSGAL, combined with the
longer wavelength data from HIGAL, it is, in princple, possible to
distinguish which objects are clouds and which are holes.

\subsection{Input catalogue}
This study uses candidate IRDCs in the inner regions of the Galactic
Plane (the first and fourth quadrants). We use two catalogues based on
MIR data from the MSX and \spitzer\ surveys (\citet{Simon06,PF09}),
and add to that FIR data from the \herschel HI-GAL survey. The
\citet{Simon06} catalogue (henceforth S06) uses 8\,\mic\ MSX data to
identify over 10000 IRDCs in the region defined by $|l| < 90^{\circ}$
and $|b|<5^{\circ}$. This was restricted to IRDCs greater than 36'' in
size (limited by the 20'' resolution of MSX) and with a sensitivity of
1.2\,MJy/sr. The \citet{PF09} catalogue (henceforth PF09), used
\spitzer\ 8 and 24\,\mic\ data in the region defined by $10^{\circ} <
|l| < 65^{\circ}$ and $|b|<1^{\circ}$. While \spitzer\ data had better
resolution and sensitivity (2'' and 0.3 MJy/sr at 8\,\mic), it covered
a smaller region of the Galactic Plane. The \higal\ survey covers the
full Galactic Plane within $|b|<1^{\circ}$, with a resolution of
$\sim18''$ at 250\,\mic.

Sources included in this study require coverage at both 8 and
24\,\mic. They are selected from PF09, along with sources from S06
which are not within 25'' of a PF09 source. This results in 9931
sources from PF09 (4123 in the range $0 < l < 90$ and 5808 in the
range $270 < l < 360$) and 5731 from S06 (2672 in the range $0 < l <
90$ and 3059 in the range $270 < l < 360$).

\section{Analysis}
Brief outline of analysis

\subsection{Milky Way Project}
The Milky Way Project\footnote{http://www.milkywayproject.org} was established in 2010 as a citizen science interface to data from the \emph{Spitzer} GLIMPSE survey primarily as a search for `bubbles' associated with massive star formation. This effort was successful, and a catalogue of more than 5000 such bubbles which expanded on previous efforts by professional astronomers was published by \citet{Simpsonetal} and used for a statistical analysis of bubble distribution by \citet{Kendrewetal}. Inspired by this success, a second interface was added to the site in order to address the problem of identifying true IRDCs.

As with the previous interface, this new part of the site\footnote{http://www.milkywayproject.org/clouds} makes use of the Zooniverse Application Programming Interface (API) originally built for Galaxy Zoo \citep{Lintottetal} and which supports a large number of similar citizen science projects. This API is primarily responsible for serving images and recording classifications provided by volunteers, who are required to be logged in for their work to be recorded. Following a short tutorial, an image is selected from the database\footnote{Volunteers see an image they have not yet classified, selected randomly from those with the fewest classifications in the database. This algorithm for task assignment has the advantage of ensuring that images have approximately the same number of classifications at all times, facilitating preliminary data analysis.} and presented to the volunteer who may label it as a \textsc{cloud}, a \textsc{hole} or an \textsc{intermediate} case by selecting one of three buttons. 

MWP interface and initial results (or in results section?)
User and classification numbers and duration of dataset used

Raw classifications?
Histogram of results?

Thumnail examples of clouds, holes and unknowns

\subsection{Experts and Training data}
Definition of training data definition

Thumbnails of training data and classifications

Expert versus general results (plot)

\subsection{Analysis sequence}
The procedure
Growth charts
Results of MC runs
Any threshholds


\section{Results}
Results from analyis (cloudiness chart)

Histogram of classifications before \& after

Thumnail examples of clouds, holes and unknowns

Full table of results

\section{Conclusions}


\section{Acknowledgements}
\chck{Zooniverse acknowledgements}

{\em Herschel} is an ESA space observatory with science instruments
provided by European-led Principal Investigator consortia and with important
participation from NASA.

SPIRE has been developed by a consortium of institutes led by Cardiff
Univ. (UK) and including: Univ. Lethbridge (Canada); NAOC (China);
CEA, LAM (France); IFSI, Univ. Padua (Italy); IAC (Spain); Stockholm
Observatory (Sweden); Imperial College London, RAL, UCL-MSSL, UKATC,
Univ. Sussex (UK); and Caltech, JPL, NHSC, Univ. Colorado (USA). This
development has been supported by national funding agencies: CSA
(Canada); NAOC (China); CEA, CNES, CNRS (France); ASI (Italy); MCINN
(Spain); SNSB (Sweden); STFC, UKSA (UK); and NASA (USA).

This research made use of APLpy, an open-source plotting package for
Python hosted at http://aplpy.github.com

\end{document}
